% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Anas Abou Allaban}
\newcommand{\CVTitle}{Anas Abou Allaban's CV}
% \newcommand{\CVNote}{CV compiled on {\today} for Brian Albrecht}
\newcommand{\CVWebpage}{abouallaban.info}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
10 Lauren Lane, Mansfield, MA, 02048 USA
\,\SubBulletSymbol\,
+1\,(508)\,901-7922
\par
% Email
\href{mailto:aabouallaban@protonmail.com}
{aabouallaban@protonmail.com}
\,\SubBulletSymbol\,
% Site
\href{http://abouallaban.info}
{\url{\CVWebpage}}
\, \SubBulletSymbol\,
% Git
\href{http://github.com/piraka9011}
{\url{github.com/piraka9011}}
\end{SubTitle}

\begin{Body}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

%% RIVeR Lab %%
\Entry
\href{http://robot.neu.edu/}
{\textbf{Robotics and Intelligent Vehicles Research Lab}},
Northeastern University

\Gap
\textit{Research Assistant}, Advisor: 
\href{tpadir.info}{\textbf{Prof. Taskin Padir}}
\hfill
\DatestampYM{2016}{07} -- Present
\BulletItem 
Worked with \textbf{\href{https://www.linkedin.com/in/velin-dimitrov/}{Dr. Velin Dimitrov}} to support his thesis on human-in-the-loop cyber-physical systems. Designed an experiment using a Turtlebot \& Clearpath Jackal to analyze the performance of a blended shared control architecture and its effect on human-robot team performance.
\begin{Detail}
	\Item
	Presented at \textbf{RISE 2017} and submitted to \textbf{ICRA 2019}.
\end{Detail}
\BulletItem 
Worked with PhD student \href{http://kelestemur.com/}{\textbf{Tarik Kelestemur}} to lead \& mentor a group of undergraduate students to support the development of \href{http://www.toyota-global.com/innovation/partner_robot/family_2.html}{Toyota's Human Support Robot}. I designed \& developed \href{http://wiki.ros.org/dialogflow_ros}{\textbf{DialogflowROS}}, a speech interface system with hotwords and context sensitive grammar using Google's Speech \& NLP APIs. Our team participated in Robocup@Home2017/18 and was invited to the World Robot Summit 2018. We placed 4th internationally and best in the USA.
\begin{Detail}
	\Item
	Presented at \href{http://ieee.scripts.mit.edu/conference/}{\textbf{MIT IEEE URTC 2018}}.
\end{Detail}
\SectionSpace

%% IHMS Lab %%

\Entry
\href{http://www1.coe.neu.edu/~yilin/ihmslab.html}
{\textbf{Integrated Human-Machine Systems Lab}},
Northeastern University

\Gap
\textit{Research Assistant}, Advisor:
\href{http://www1.coe.neu.edu/~yilin/director.html}{\textbf{Prof. Yingzi Lin}}
\hfill
\DatestampYMD{2015}{11}{01} --
\DatestampYMD{2016}{06}{01}
\BulletItem
Supported graduate student Li Wang's project on the use of EEG sensors to interface with robots using SVM classifiers. 
\begin{Detail}
	\Item
	Submitted to \href{http://acc2016.a2c2.org/}{\textbf{ACC 2016}}
\end{Detail}
\BulletItem
Researched the effects of cold pain on physiological signals by designing an experiment to measure pain tolerance.
\begin{Detail}
	\Item
	Presented at \href{https://www.northeastern.edu/rise/}{\textbf{RISE 2016}}. 
\end{Detail}

%% MIT MRL %%

\Entry
\href{http://mechatronics.mit.edu/}
{\textbf{Mechatronics Research Lab}},
Massachusetts Institute of Technology

\Gap
\textit{Research Intern}
\hfill
\DatestampYM{2014}{09} --
\DatestampYM{2015}{02}
\BulletItem
Supported \href{http://meche.mit.edu/people/faculty/youcef@mit.edu}{\textbf{Prof. Kamal El-Toumi}} and \href{https://www.linkedin.com/in/iman-soltani-bozchalooi-31a7b281/}{\textbf{Dr. Iman Soltani's}} project on car and pedestrian detection in autonomous vehicles for Ford through a literature survey. Trained BRISK, FAST, and SURF classifiers using Matlab and analyzed performance, accuracy, and tradeoffs of each feature extractor.

%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:OtherWorkExperience}

%% Arcelik %%

\Entry
\href{http://www.arcelikas.com/page/69/Technology_and_Innovation}
{\textbf{Ar\c{c}elik}}, 
Istanbul, Turkey

\Gap
\textit{Robotics R\&D Intern}
\hfill
\DatestampYM{2018}{07} -- Present
\BulletItem
Conducted a market analysis and systematic review on state-of-the-art literature in home robotics and smart homes. Presented results to executives and research managers.
\BulletItem
Designed and prototyped proof-of-concept robot technologies including a clutter cleaning robot.
\BulletItem
Wrote a technology road map for a future research/product ecosystem at Ar\c{c}elik, creating projects for future coops as well.
\SectionSpace

%% iRobot %%

\Entry
\href{http://www.irobot.com}
{\textbf{iRobot}},
Bedford, MA

\Gap
\textit{Lead Systems Test Intern}
\hfill
\DatestampYM{2017}{05} -- \DatestampYM{2012}{12}
\BulletItem
Designed an optoelectronic test fixture for iRobot's home-based product line which identified critical docking issues in old generation Roombas. %Updated optoelectronics resulted in increased docking performance across the product line.
\BulletItem
Trained \& assisted interns with on-boarding, power tools, software, and electronics. Ran workshops to train interns on tools like ROS.
\BulletItem
Designed, built, and maintained test fixtures by programming MCUs, designing electronic circuits, and machining \& printing parts.
\BulletItem
Wrote a shape, color, and face detection program for iRobot's future STEM product using OpenCV.
\BulletItem
Wrote LabView programs that collected sensor data from iRobot's future products to validate new features.
\SectionSpace

%% Resilience %%

\Entry
\href{https://www.nbchealthcare.com/}
{\textbf{Neuro Behavioral Center}},
Walpole, MA

\Gap
\textit{Partner \& Co-Founder}
\hfill
\DatestampYM{2014}{08} -- Present
\BulletItem
Established a psychiatric clinic, setting up operations including finance, HR, and legal structure.
\BulletItem
Wrote employee training manual, handbook, and company policy.
\BulletItem
Currently focused on monitoring financial performance and clinic budget.\\

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

%% Northeastern %% .

\Entry
\href{http://www.northeastern.edu}
{\textbf{Northeastern University}},
Boston, MA

\Gap
B.S. in 
\href{http://www.ece.neu.edu/}
{Electrical and Computer Engineering}
\hfill
Exp. Apr 2019
\begin{Detail}
	\SubBulletItem
	Concentration: Robotic systems, kinematics, and dynamics.
	\SubBulletItem
	Minor: Mathematics
	\SubBulletItem
	Dean's List (All Semesters) | Cumulative GPA: 3.89 / 4.0
\end{Detail}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
\textbf{Programming}
\BulletItem
\textbf{Experienced (3+ years)}
\newline
C\textbackslash C++, Python, MATLAB, Simulink, HTML\textbackslash CSS.

\BulletItem
\textbf{Proficient (1+ years)}
\newline
JavaScript,
LabView,
Verilog,
Bash Scripting,
MIPS Assembly,
{\LaTeX}.

\textbf{Platforms}
\newline
ROS, Linux, Tensorflow, Scipy, Numpy, Pandas, Matplotlib, OpenCV, PCL, Git, NI DAQs

\textbf{Applications}
\newline
OrCAD/PSpice, Eagle PCB, Solidworks, Jira (Agile), AutoCAD.

\textbf{Fabrication}
\newline
CNC Milling, Manual Milling \& Turning, Soldering \& Crimping, Rapid Prototyping.

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
%\begingroup
%\renewcommand{\MaxNumberedItem}{[8888]}

\BigGap
\NumberedItem{[1]}
{\underline{A. Abou Allaban}, V. Dimitrov, and T. Padir, 
``A blended human-robot shared control framework to handle drift and latency,``
Submitted to \textit{Int. Conf. on Robotics \& Automation}, 2019.}

\Gap
\NumberedItem{[2]}
{\underline{A. Abou Allaban}, T. Kelestemur, N. Yokoyama, and T. Padir,
	``A System Architecture for Mobile Robots in a Home Environment: Team Northeastern’s Approach for Robocup@Home,``
	Presented at \textit{IEEE MIT Undergraduate Research Tech. Conf.}, 
	Boston, MA, USA,
	\DatestampYM{2018}{10}.}

\Gap
\NumberedItem{[3]}
{\underline{A. Abou Allaban} and T. Padir,
	``Performance Evaluation of a Blended Shared Controller in Human-Robot Teams,''
	in \textit{Research and Innovation Student Expo},
	Boston, MA, USA,
	\DatestampYM{2017}{4}.}

\Gap
\NumberedItem{[4]}
{Y. Lin, L. Wang, and \underline{A. Abou Allaban},
``A Feature Extraction and Classification Algorithm for ERD/ERS-based classification in a Brain-Computer Interface system,``
in \textit{Proceedings of the American Control Conference},
Boston, MA,
\DatestampYM{2016}{07}.}

%\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\Gap
Northeastern Presidential Global Scholarship
\hfill
\DatestampYM{2018}{07}
\begin{Detail}
Award given to Northeastern students with an outstanding academic record seeking to pursue a global co-op opportunity.
\end{Detail}
\SectionSpace

\Gap
Northeastern Excellence Scholarship
\hfill
\DatestampY{2015} -- 
\DatestampY{2019}
\begin{Detail}
Merit-based scholarship awarded for students who have academically excelled in their coursework.
\end{Detail}

\Gap
Best/Outstanding Delegate
\hfill
\DatestampYM{2014}{11} --
\DatestampYM{2015}{07}
\begin{Detail}
Awarded to MUN delegates that showcase the best debating and leadership skills.
\end{Detail}
\begin{Detail}
Awarded at MITMUNC, UMass Amherst MUN, UNAGB MAL \& RMUN.
\end{Detail}

\Gap
1st place ADNOC Regional Science Fair
\hfill
\DatestampYM{2014}{01}
\begin{Detail}
Awarded for designing a system for controlling a robot with gestures using a Microsoft Kinect.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Affiliations\newline
\& Activities}
{Professional Affiliations \& Activities}
{PDF:ProfessionalAffiliationsActivities}

\Entry
\textbf{IEEE RAS - Northeastern Student Chapter},
Boston, MA
\Gap
\textit{Founder, President}
\hfill
\DatestampYM{2018}{07} --
Present
\begin{Detail}
\Item
Established an IEEE RAS Student Branch Chapter. Conducted workshops on robotic technologies, invited speakers from industry \& academia, and collaborated with research labs to connect students with research projects.
\end{Detail}

\Entry
\textbf{Al-Noor Academy Model UN},
Mansfield, MA
\Gap
\textit{Founder, Advisor}
\hfill
\DatestampYM{2014}{03} --
Present
\begin{Detail}
\Item
Established an MUN organization at the Glenelg School of Abu Dhabi, paving the way for a major student led
group with 150+ members. A similar organization was introduced at Al-Noor Academy. Currently assisting in an advisory role.
\end{Detail}

\Entry
\textbf{IEEE HKN - Gamma Beta Chapter},
Boston, MA
\Gap
\textit{Member, Tutor}
\hfill
\DatestampY{2018} --
Present
\begin{Detail}
\Item
Tutor for Northeastern's upper-level ECE classes as part of IEEE-HKN's tutoring initiative.
\end{Detail}

\Entry
\textbf{Tau Beta Pi Engineering Honor Society},
Boston, MA
\hfill
\DatestampY{2018} --
Present

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Native: English, Arabic

\Gap
\BulletItem
Intermediate: Turkish


% %%%%%%%%%%%%%%%%%%%%%%%
% %% PERSONAL PROJECTS %%
% %%%%%%%%%%%%%%%%%%%%%%%

% \Section
% {Personal Projects}
% {Personal Projects}
% {PDF:Personal Projects}

% \Entry
% \BulletItem Built a Millright CNC machine. 
% \BulletItem NAS server and IoT sensors using Rasberry Pis. 
% \BulletItem Gesture-detecting robot with the Kinect (See ADNOC award). 
% \BulletItem Iron Man glove using an Arduino Wave Shield, EMG sensors, and LEDs.

% %%%%%%%%%%%%%%%
% %% INTERESTS %%
% %%%%%%%%%%%%%%%

% \Section
% {Interests}
% {Interests}
% {PDF:Interests}

% \Entry
% Obstacle Course Running,
% Powerlifting,
% Trail running \& biking.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

% \Section
% {References}
% {References}
% {PDF:References}

% \BigGap
% \BulletItem
% \textbf{Dr Velin Dimitrov}
% \newline
% Systems Engineer
% \newline
% Toyota Research Institute
% \newline
% 1 Kendall Square, Binney St Building 100, Suite 1-201, Cambridge, MA 02139
% \newline
% \href{mailto:v.dimitrov@gmail.com}
% {v.dimitrov@gmail.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MULTILINGUAL UNICODE EXAMPLES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
% {Multilingual Unicode Examples}
% {Multilingual Unicode Examples}
% {PDF:MultilingualUnicodeExamples}

% \BulletItem
% Assortment of unicode characters from
% \href{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}
% {\url{http://www.ltg.ed.ac.uk/~richard/unicode-sample.html}}

% \begin{Detail}
% \Item
% \textbf{Latin Extended-A}
% Ā ā Ă ă Ą ą Ć ć Ĉ ĉ Ċ ċ Č č Ď ď Đ đ Ē ē Ĕ ĕ Ė ė Ę ę Ě ě Ĝ ĝ Ğ ğ Ġ ġ Ģ ģ Ĥ ĥ Ħ ħ Ĩ ĩ Ī ī Ĭ ĭ Į į İ ı Ĳ ĳ Ĵ ĵ
% \textbf{Latin Extended-B}
% ƀ Ɓ Ƃ ƃ Ƅ ƅ Ɔ Ƈ ƈ Ɖ Ɗ Ƌ ƌ ƍ Ǝ Ə Ɛ Ƒ ƒ Ɠ Ɣ ƕ Ɩ Ɨ Ƙ ƙ ƚ ƛ Ɯ Ɲ ƞ Ɵ Ơ ơ Ƣ ƣ Ƥ ƥ Ʀ Ƨ ƨ Ʃ ƪ ƫ Ƭ ƭ Ʈ Ư ư Ʊ Ʋ Ƴ ƴ Ƶ
% \textbf{Latin Extended Additional}
% Ḁ ḁ Ḃ ḃ Ḅ ḅ Ḇ ḇ Ḉ ḉ Ḋ ḋ Ḍ ḍ Ḏ ḏ Ḑ ḑ Ḓ ḓ Ḕ ḕ Ḗ ḗ Ḙ ḙ Ḛ ḛ Ḝ ḝ Ḟ ḟ Ḡ ḡ Ḣ ḣ Ḥ ḥ Ḧ ḧ Ḩ ḩ Ḫ ḫ Ḭ ḭ Ḯ ḯ Ḱ ḱ Ḳ ḳ Ḵ ḵ
% \textbf{Greek}
% ʹ ͵ ͺ ; ΄ ΅ Ά · Έ Ή Ί Ό Ύ Ώ ΐ Α Β Γ Δ Ε Ζ Η Θ Ι Κ Λ Μ Ν Ξ Ο Π Ρ Σ Τ Υ Φ Χ Ψ Ω Ϊ Ϋ ά έ ή ί ΰ α β γ δ ε ζ η θ
% \textbf{Cyrillic}
% Ё Ђ Ѓ Є Ѕ І Ї Ј Љ Њ Ћ Ќ Ў Џ А Б В Г Д Е Ж З И Й К Л М Н О П Р С Т У Ф Х Ц Ч Ш Щ Ъ Ы Ь Э Ю Я а б в г д е ж з
% \textbf{Hebrew}
% א ב ג ד ה ו ז ח ט י ך כ ל ם מ ן נ ס ע ף פ ץ צ ק ר ש ת װ ױ ײ ֝ ֞ ֟ ֠ ֡ ֣ ֤ ֥ ֦ ֧ ֨ ֩ ֪ ֫ ֬ ֭ ֮ ֯ ְ ֱ ֒ ֓ ֔
% \textbf{Armenian}
% {\UseSecondaryFont
% Ա Բ Գ Դ Ե Զ Է Ը Թ Ժ Ի Լ Խ Ծ Կ Հ Ձ Ղ Ճ Մ Յ Ն Շ Ո Չ Պ Ջ Ռ Ս Վ Տ Ր Ց Ւ Փ Ք Օ Ֆ ՙ ՚ ՛ ՜ ՝ ՞ ՟ ա բ գ դ ե զ}
% \textbf{Thai}
% {\UseSecondaryFont
% ก ข ฃ ค ฅ ฆ ง จ ฉ ช ซ ฌ ญ ฎ ฏ ฐ ฑ ฒ ณ ด ต ถ ท ธ น บ ป ผ ฝ พ ฟ ภ ม ย ร ฤ ล ฦ ว ศ ษ ส ห ฬ อ ฮ ฯ ะ ั า ำ ิ}
% \end{Detail}

% % Manual page break.
% \newpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% THIS IS A SECTION WITH USAGE NOTES %%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % Declare a new group to limit the scope of \color to this section.
% \begingroup
% \color{red}

% \Section
% {This is a\newline
% Section\newline
% With\newline
% Usage Notes}
% {This is a Section With Usage Notes (For PDF Bookmark)}
% {PDF:ThisIsASectionWithUsageNotes:ForPDFLink}

% \SubSection
% {This is a SubSection}
% {This is a SubSection (For PDF Bookmark)}
% {PDF:ThisIsASubSection:ForPDFLink}

% \BigGap
% \BulletItem
% Use \CodeCommand{Section\{a\}\{b\}\{c\}} and
% \CodeCommand{SubSection\{a\}\{b\}\{c\}}
% to create sections and subsections, where
% \Code{a} is the heading displayed on the page,
% \Code{b} is the PDF bookmark heading, and
% \Code{c} is the internal PDF link (must be unique).
% Sections and subsections will appear in the PDF bookmarks.
% Note the CamelCase command names.

% \Gap
% \BulletItem
% Use
% \CodeCommand{Entry},
% \CodeCommand{BulletItem},
% \CodeCommand{SubBulletItem},
% \CodeCommand{Item},
% \CodeCommand{SubItem},
% \CodeCommand{NumberedItem},
% etc.,
% to create entries in the main body of the CV.

% \Gap
% \BulletItem
% Enclose entry details between
% \CodeCommand{begin\{Detail\}} and
% \CodeCommand{end\{Detail\}}
% so that they are typeset in a smaller font.
% \begin{Detail}
% \Item
% This is an example of entry detail text enclosed in a \Code{Detail} environment.
% \end{Detail}

% \Gap
% \BulletItem
% Use \CodeCommand{Gap} and \CodeCommand{BigGap} to insert vertical spaces between entries to improve layout.

% \BigGap
% \SubSection
% {This is Another SubSection}
% {This is Another Subsection (For PDF Bookmark)}
% {PDF:ThisIsAnotherSubSection:ForPDFLink}

% \BigGap
% \Entry
% This is a plain \CodeCommand{Entry},
% followed by an \CodeCommand{hfill} and a date range
% \hfill
% \DatestampYM{2015}{10} --
% \DatestampYM{2015}{12}

% \Gap
% \BulletItem
% This is a \CodeCommand{BulletItem}.
% \Item
% This is an \CodeCommand{Item}, which has no bullet.
% Note the alignment with the \CodeCommand{BulletItem} above.

% \Gap
% \SubBulletItem
% This is a \CodeCommand{SubBulletItem}.
% \SubItem
% This is a \CodeCommand{SubItem}, which has no bullet.
% Note the alignment with the \CodeCommand{SubBulletItem} above.

% \Gap
% \NumberedItem{[42]}
% This is a \CodeCommand{NumberedItem}.
% Change the value of the macro \CodeCommand{MaxNumberedItem} to adjust the indentation width.

% \BigGap
% \SubSection
% {Line, Paragraph, and Page Breaks}
% {Line, Paragraph, and Page Breaks (For PDF Bookmark)}
% {PDF:LineParagraphAndPageBreaks:ForPDFLink}

% \BigGap
% \BulletItem
% To create a new line within the same paragraph (i.e., preserving the same paragraph indentation), use \CodeCommand{newline} instead of \CodeCommand{\textbackslash};
% the latter will reset the paragraph indentation.

% \Gap
% \BulletItem
% To create a new paragraph, use \CodeCommand{par} or simply leave an empty line.
% Paragraph indentations (from
% \CodeCommand{Entry},
% \CodeCommand{BulletItem},
% \CodeCommand{SubBulletItem},
% \CodeCommand{Item},
% \CodeCommand{SubItem},
% \CodeCommand{NumberedItem},
% etc.) do not carry across different paragraphs.

% \Gap
% \BulletItem
% To create a new page, use \CodeCommand{newpage}.

% \BigGap
% \SubSection
% {Dates}
% {Dates (For PDF Bookmark)}
% {PDF:Dates:ForPDFLink}

% \BigGap
% \BulletItem
% Use the following macros to specify and display dates consistently:
% \SubBulletItem
% \CodeCommand{DatestampYMD\{yyyy\}\{MM\}\{dd\}}
% (e.g., \CodeCommand{DatestampYMD\{2008\}\{01\}\{15\}})
% \SubBulletItem
% \CodeCommand{DatestampYM\{yyyy\}\{MM\}}
% (e.g., \CodeCommand{DatestampYM\{2008\}\{01\}})
% \SubBulletItem
% \CodeCommand{DatestampY\{yyyy\}}
% (e.g., \CodeCommand{DatestampY\{2008\}})

% \Gap
% \BulletItem
% Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
% \SubBulletItem
% \Code{MMMyyyy} (``Jan~2008'')
% \SubBulletItem
% \Code{ddMMMyyyy} (``15~Jan~2008'')
% \SubBulletItem
% \Code{MMMMyyyy} (``January~2008'')
% \SubBulletItem
% \Code{ddMMMMyyyy} (``15~January~2008'')
% \SubBulletItem
% \Code{yyyyMMdd} (``2008-01-15'')
% \SubBulletItem
% \Code{yyyyMM} (``2008-01'')
% \SubBulletItem
% \Code{yyyy} (``2008'')



\end{Body}

% %%%%%%%%%%%
% % CV NOTE %
% %%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
% [\textit{\CVNote}]

\end{document}
